%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}


%---------------------------------------------------------
  \cventry
    {Enginuity Consulting Ltd.} % Organization
    {Design Engineer} % Job title
    {Vancouver, Canada} % Location
    {Jun. 2017 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {  }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Enercorp Sand Solutions} % Organization
    {Sr. Mechanical Designer} % Job title
    {Calgary, Canada} % Location
    {Apr. 2012 - Mar. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented heat transfer and energy models for line heaters, chillers, and buildings}
        \item {Utilized novel mixed fluid and precipitate flow models for sizing pressure vessels and sand filters}
        \item {Drafted US Patent application for combination filter that maximized retention time, filter diameter, and strength}
        \item {Mentored junior engineers and emphasized design best practices}
      \end{cvitems}
    }

\cvsubsection{Non-Technical Work Experience}

%---------------------------------------------------------
  \cventry
    {Spanish Banks Contracting} % Organization
    {Carpenter} % Job title
    {Vancouver, Canada} % Location
    {May 2017 - September 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Renovated, framed, and sided residential building envelopes to repair and prevent future water damage}
        \item {Managed labourers to build their skills in the trades and to improve their jobsite productivity}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Ocean Wise (Vancouver Aquarium)} % Organization
    {Marine Mammal Rescue} % Job title
    {Seoul, S.Korea} % Location
    {May. 2017 - Sep. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Cared for injured and abandoned infant seals, sea lions, and sea otters}
        \item {Prepared milk matrix, gavage fed, measured and dosed medication, and kept facilities sanitary}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Aero Trading Co. Ltd.} % Organization
    {Commercial Fisherman} % Job title
    {Prince Rupert, Canada} % Location
    {Jun. 2016 - Aug. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
          \item {Sustainably and ethically caught Coho and Chinook salmon with long line trolling boat and MaxSea navigation software}
          \item {Ensured proper mechanical maintenance of 70 year old vessel}
        \end{cvitems}
        }

%---------------------------------------------------------
  \cventry
    {SAIT Polytechnic} % Organization
    {Peer Tutor} % Job title
    {Calgary, Canada} % Location
    {Sep. 2011 - Apr. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Planned and taught weekly review sessions for Math, Dynamics, and Statics}
        \item {Sessions attended by groups of up to 6 civil and mechanical engineering students}
      \end{cvitems}
    }

%---------------------------------------------------------

\cvsubsection{Design Projects}

%---------------------------------------------------------
  \cventry
    {Femur Fracture Traction Project, Project Designer} % Project title
    {UBC Biomedical Engineering Student Team} % Course
    {Vancouver, Canada} % Location
    {Sep. 2016 - Sep. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Lead hardware prototype development and solid model designs in a team of lower year engineering students}
        \item {Designed a one size fits all brace to stabilize a femur fracture and distribute pressure for long term use while also performing traction to promote bone healing}
        \item {Finalist in Medical Device Design Competition at Blusson Spinal Cord Centre}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Prosthetic Leg for Large Dog} % Project title
    {UBC Biomedical Engineering Student Team} % Course
    {Vancouver, Canada} % Location
    {Sep. 2017 - Apr. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed novel prosthetic leg for rehabilitation of large dog with amputated hind leg}
        \item {Device would allow for sitting, standing, and exercise to prevent arthritis}
    }

%---------------------------------------------------------
  \cventry
    {Pulsejet UAV} % Project title
    {MECH 328} % Course
    {Vancouver, Canada} % Location
    {Sep. 2017 - Dec. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed UAV to transport medical TB samples from rural Rwanda to medical centre}
        \item {Created medical sample storage and destruction mechanism parametrically with the fuselage of aircraft}
    }


%---------------------------------------------------------
\end{cventries}
